\documentclass[13pt,a4paper]{report}
\usepackage{listings}

\begin{document}
\begin{titlepage}
	\centering
	\vspace{2cm}
	{\huge\bfseries Report labwork 11: Design a database \par}
	\vspace{2cm}
	{\Large\itshape Loc Thi Thuy Linh\par}
	\vfill
	supervised by\par
	Nghiem Thi Phuong \& Tran Giang Son \textsc{Brown}
	ICT Department, USTH\par
	\vfill
% Bottom of the page
	{\large \today\par}
\end{titlepage}

\begin{itemize}

\item Problem:
\indent A Non-Government Organization (NGO) wants to prepare a database for
all its projects. It has diverse head offices in several countries which take
manage and coordinate the projects of that country.
\\
\indent On head offices, an identifier, the city and country where it is located, its
address, a phone number and the name of the director are stored. Every
head office manages a set of projects, with a code, a title, dates of beginning
and end, the assigned budget and the name of the person in charge. One
project is formed by a set of actions that can affect to several cities.
\\
\indent We want to know what actions are realised in each city, storing its name,
country and no of inhabitants. We also need an identifier to differentiate
them. Also there is wished the investment of the project that corresponds to
the city and a small description of the action.


\section{ How you made up the structure (those conceptual/logical/physical models) }


\section{ SQL commands to create the database and outputs }

\begin{lstlisting}
		+-----------------------------+
		|           product           |
		+-----------------------------+
		|          pro_id             |
		|          description        |
		|          price              |
		+-----------------------------+

		

\end{lstlisting}




\end{itemize}

\end{document}
